\LARGE \bf Grupo Bimbo Inventory Demand Data Science Report

### 2024-07-15 src/data-science-project/data_science_project/docs/paper/paper.tex
Models
Documents 95 percent

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{url}

@@

\subsection{Modeling}
Two machine learning models were employed:
\begin{itemize}
        \item XGBoost: A gradient boosting framework optimized for performance.
        \begin{itemize}
                \item $\textbf{Parameters}$: $n\_estimators=100$, \\$max\_depth=8$, $learning\_rate=0.1$, $subsample=0.8$, $colsample\_bytree=0.8$, $random\_state=42$.
        \end{itemize}
        \item Random Forest: An ensemble learning method using multiple decision trees.
        \begin{itemize}
                \item $\textbf{Parameters}$: $n\_estimators=100$, \\$max\_depth=10$, $random\_state=42$.
        \end{itemize}
\end{itemize}

@@

\section{RESULTS}
The performance of the XGBoost and Random Forest models was evaluated based on the RMSE. The XGBoost model achieved an RMSE of X, indicating better predictive accuracy compared to the Random Forest model, which had an RMSE of Y. The superior performance of XGBoost can be attributed to its ability to handle complex interactions between features and its robustness to overfitting. The inclusion of external economic indicators, such as bi-weekly inflation rates and the consumer confidence index, further enhanced the model's predictive capabilities. Detailed performance metrics, including precision, recall, and F1-score, were also computed to provide a comprehensive evaluation of the models.

>>>>

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{float} 
\usepackage{graphicx}
\usepackage{url}

@@

\subsection{Modeling}
Two machine learning models were employed:
\begin{itemize}
        \item XGBoost: A gradient boosting framework optimized for performance.
        \begin{itemize}
                \item $\textbf{Parameters}$: $n\_estimators=200$, $max\_depth=8$, $learning\_rate=0.2$, $subsample=0.9$, $colsample\_bytree=0.8$, $n\_jobs=-1$, and $random\_state=42$.
        \end{itemize}
        \item Random Forest: An ensemble learning method using multiple decision trees.
        \begin{itemize}
                \item $\textbf{Parameters}$: $n\_estimators=110$, $min\_samples\_split=10$, $min\_samples\_leaf=5$, $n\_jobs=-1$, and $random\_state=42$.
        \end{itemize}
\end{itemize}

@@

\section{RESULTS}
The performance of the XGBoost and Random Forest models was evaluated based on the RMSE. The Random Forest model achieved an RMSE of X, indicating better predictive accuracy compared to the XGBoost model, which had an RMSE of Y. The superior performance of Random Forest can be attributed to its ability to handle high-dimensional data and its robustness to overfitting. The inclusion of external economic indicators, such as bi-weekly inflation rates and the consumer confidence index, further enhanced the model's predictive capabilities.

\begin{figure}[H] 
        \begin{center}
        \centering
        \includegraphics[width=0.9\textwidth]{images/comparison.jpg}
        \caption{Actual vs Predict Adjusted Demand}
        \end{center}
\end{figure}

\begin{figure}[H] 
        \begin{center}
        \centering
        \includegraphics[width=0.9\textwidth]{images/comparisonxg.jpg}
        \caption{Actual vs Predict Adjusted Demand}
        \end{center}
\end{figure}
